
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
%\secretlevel{绝密} \secretyear{2100}

\ctitle{多核可扩展操作系统内核关键技术的研究与实现}
% 根据自己的情况选，不用这样复杂
\makeatletter
\ifthu@bachelor\relax\else
  \ifthu@doctor
    \cdegree{工学博士}
  \else
    \ifthu@master
      \cdegree{工学硕士}
    \fi
  \fi
\fi
\makeatother


\cdepartment[计算机]{计算机科学与技术系}
\cmajor{计算机科学与技术}
\cauthor{陈宇恒} 
\csupervisor{陈渝~副教授}
% 如果没有副指导老师或者联合指导老师，把下面两行相应的删除即可。
%\cassosupervisor{陈文光教授}
%\ccosupervisor{某某某教授}
% 日期自动生成，如果你要自己写就改这个cdate
%\cdate{\CJKdigits{\the\year}年\CJKnumber{\the\month}月}

% 博士后部分
% \cfirstdiscipline{计算机科学与技术}
% \cseconddiscipline{系统结构}
% \postdoctordate{2009年7月——2011年7月}

\etitle{TODO: Implementation and Analysis of Operating System on Multicore
System} 
% 这块比较复杂，需要分情况讨论：
% 1. 学术型硕士
%    \edegree：必须为Master of Arts或Master of Science（注意大小写）
%              “哲学、文学、历史学、法学、教育学、艺术学门类，公共管理学科
%               填写Master of Arts，其它填写Master of Science”
%    \emajor：“获得一级学科授权的学科填写一级学科名称，其它填写二级学科名称”
% 2. 专业型硕士
%    \edegree：“填写专业学位英文名称全称”
%    \emajor：“工程硕士填写工程领域，其它专业学位不填写此项”
% 3. 学术型博士
%    \edegree：Doctor of Philosophy（注意大小写）
%    \emajor：“获得一级学科授权的学科填写一级学科名称，其它填写二级学科名称”
% 4. 专业型博士
%    \edegree：“填写专业学位英文名称全称”
%    \emajor：不填写此项
\edegree{TODO DEGREE} 
\emajor{Computer Science and Technology} 
\eauthor{Chen Yuheng} 
\esupervisor{Associate Professor Chen Yu} 
%\eassosupervisor{Chen Wenguang} 
% 这个日期也会自动生成，你要改么？
% \edate{December, 2005}

% 定义中英文摘要和关键字
\begin{cabstract}

随着多核架构计算机技术的迅猛发展，如何使用新方法提高操作系统内核的多核可扩展性性能,已经成
为操作系统领域关注的重要课题,具有较高的研究价值和现实意义。
本文的主要工作包括：对Linux 虚拟内存管理系统的多核竞争瓶颈问题和MIT提出的RadixVM相关多核优化技术
进行了深入研究；基于RadixVM提出了一种针对对象引用计数器和简化 Posix 标准的操作系统虚
拟内存管理子系统的建模方法，并在可交换性原理的基础上通过KLEE 符号执行引擎设计了
求解操作系统模型中可扩展实现存在条件的方法；基于分析出的可扩展性存在条件设计实现了一个
支持 AMD64 NUMA 多核架构的操作系统内核原型ucore-mp；实现了一款基于 QEMU 模拟器的全系统性能分析工具 QProf,用于方便地测试
操作系统内核性能。实验结果表明，ucore-mp引用技术多核优化技术在多核硬件平台上比一般原子操作的扩展性性能加速比提高了73\%以上。

\end{cabstract}

\ckeywords{操作系统, 符号执行, 多核可扩展性}

\begin{eabstract} 
	
	As the development of microelectronic technology, multicore scalability on hardware systems has become a big challenge to the operating system developers.  Designing new mechanism to improve the multicore scalability is an attractive topic in both industry and academia.
	This paper analyzes the scalability bottleneck in the virtual memory subsystem of Linux, and research into several optimization technology on multicore 
	systems, such as RadixVM from MIT. Based on these technologies, we propose a modeling method for reference counter and
	virtual memory subsystem conforming to a simplified Posix specification.  Furthermore, we combine KLEE symbolic execution engine and the commutability rule 
	to prove the existence of multicore scalable implementations of system interfaces. Based on the theory, we develop a modern operating system kernel ucore-mp on
	AMD64 NUMA multicore  architecture. Finally, a QEMU-based full system profiler QProf is developed to find potential performance problems in the kernel. An Experimental evaluation shows s performance improvements of 73\% or more with ucore-mp reference counter implementation, compared to atomic operations.
\end{eabstract}

\ekeywords{Operating System, Symbolic Execution, Scalability}
